Structured Versus Decorated Cospans

### 2020-11-23 cospans.tex
small edits in intro

An `open system' is any sort of system that can interact with the outside world.  Experience has shown that open systems are nicely modeled using cospans \cite{CourserThesis, FongThesis, PollardThesis}. A cospan in some category $\A$ is a diagram of this form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$m$};
\node (C) at (2,0) {$b$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
We call $m$ the \define{apex}, $a$ and $b$ the \define{feet}, and $i$ and $o$ the \define{legs} of the cospan.   The apex describes the system itself.  The feet describe `interfaces'  through which the system can interact with the outside world.  The legs describe how the interfaces are included in the system.   If the category $\A$ has finite colimits, we can compose cospans using pushouts: this describes the operation of attaching two open systems together in series by identifying one interface of the first with one of the second.  We can also `tensor' cospans using coproducts: this describes setting open systems side by side, in parallel.  Via these operations we obtain a symmetric monoidal double category with cospans in $\A$ as its horizontal 1-cells \cite{Courser,Niefield}.

@@

	\end{pgfonlayer}
	\begin{pgfonlayer}{edgelayer}
		\draw [style=inarrow, bend left=20, looseness=1.00] (n1) to (n2);
		\draw [style=inarrow, bend right=20, looseness=1.00] (n1) to (n3);
		\draw [style=inarrow, bend left=20, looseness=1.00] (n2) to (n4);
		\draw [style=inarrow, bend right=20, looseness=1.00] (n3) to (n4);
		\draw [style=inarrow] (n2) to (n3);
%		\draw [style=inarrow] (W) to (Water);
%		\draw [style=inarrow, bend left=40, looseness=1.00] (Water2) to (Something);
%		\draw [style=inarrow, bend right=40, looseness=1.00] (Water2) to (Something);
%		\draw [style=inarrow, bend left=40, looseness=1.00] (Something) to (A);
%		\draw [style=inarrow, bend right=40, looseness=1.00] (Something) to (B);
		\draw [style=simple] (ATL.center) to (ATR.center);
		\draw [style=simple] (ATR.center) to (ABR.center);
		\draw [style=simple] (ABR.center) to (ABL.center);
		\draw [style=simple] (ABL.center) to (ATL.center);
%		\draw [style=simple] (BTL.center) to (BTR.center);
%		\draw [style=simple] (BTR.center) to (BBR.center);
%		\draw [style=simple] (BBR.center) to (BBL.center);
%		\draw [style=simple] (BBL.center) to (BTL.center);
		\draw [style=simple] (MTL.center) to (MTR.center);
		\draw [style=simple] (MTR.center) to (MBR.center);
		\draw [style=simple] (MBR.center) to (MBL.center);
		\draw [style=simple] (MBL.center) to (MTL.center);
%		\draw [style=inputarrow] (outI) to (A);
%		\draw [style=inputarrow] (outS) to (B);
		\draw [style=inputarrow] (inI) to (n1);
		\draw [style=inputarrow] (outI') to (n4);
%		\draw [style=inputarrow] (inI') to (Water2);
%		\draw [style=inputarrow] (inS') to (Water2);
	\end{pgfonlayer}
\end{tikzpicture}
}
\]
We might hope to do this using a symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Set, \times)$ assigning to each finite set $m$ the set of all graphs with $m$ as their set of nodes    But this hope is doomed, for reasons painstakingly explained in \cite[Sec.\ 5]{BC}.  There is really a \emph{category} of graphs with $m$ as their set of nodes, and trying to treat it as a mere set does not work.

Here we present a solution to this problem.  Instead of basing the theory of decorated cospans on a symmetric lax monoidal functor $F \maps (\A, +) \to (\Set, \times)$, we use a symmetric lax monoidal pseudofunctor $F \maps (\A, +) \to (\Cat, \times)$.  In \cref{DC} we use this
data to construct a symmetric monoidal double category $F\lCsp$ in which:
\begin{itemize}
\item an object is an object of $\A$,
\item a vertical 1-morphism is a morphism of $\A$,
\item a horizontal 1-cell from $a$ to $b$ is a decorated cospan:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$m$};
\node (C) at (2,0) {$b,$};
\node (D) at (3,0) {$x \in F(m)$,};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
\item a 2-morphism is a \define{map of decorated cospans}: that is, a commutative
diagram
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a'$};
\node (B) at (1,0.5) {$m$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b'$};
\node (D) at (1,-0.5) {$m'$};
\node (E) at (3,0.5) {$x \in F(m)$};
\node (F) at (3,-0.5) {$x' \in F(m')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[right]{$g$} (C')
(A') edge node[above] {$i'$} (D)
(C') edge node[above] {$o'$} (D)
(B) edge node [left] {$h$} (D);
\end{tikzpicture}
\]
together with a morphism $\tau \maps F(h)(x) \to m'$ in $F(x')$.
\end{itemize}

In fact another solution to the problem is already known: the theory of structured cospans \cite{BC,CourserThesis}.  Given a functor $L \maps \A \to \X$, a \define{structured cospan} is a cospan in $\X$ whose feet come from a pair of objects in $\A$:
\[
\begin{tikzpicture}[scale=1.2]
\node (A) at (0,0) {$L(a)$};
\node (B) at (1,1) {$x$};
\node (C) at (2,0) {$L(b).$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C)edge node[above]{$$}(B);
\end{tikzpicture}
\]
This is another way of letting the apex have more structure than the feet.   When $\A$ and $\X$ have finite colimits and $L$ preserves them, there is a symmetric monoidal double category ${}_L \lCsp(\X)$ where:
\begin{itemize}
\item an object is an object of $\A$,
\item a vertical 1-morphism is a morphism of $\A$,
\item a horizontal 1-cell from $a$ to $b$ is a diagram in $\X$ of this form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(a)$};
\node (B) at (1,0) {$x$};
\node (C) at (2,0) {$L(b)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C)edge node[above]{$o$}(B);
\end{tikzpicture}
\]
\item a 2-morphism is a commutative diagram in $\X$ of this form:
\[
\begin{tikzpicture}[scale=1.5]
\node (E) at (3,0) {$L(a)$};
\node (F) at (5,0) {$L(b)$};
\node (G) at (4,0) {$x$};
\node (E') at (3,-1) {$L(a')$};
\node (F') at (5,-1) {$L(b')$};
\node (G') at (4,-1) {$x'$};
\path[->,font=\scriptsize,>=angle 90]
(F) edge node[above]{$o$} (G)
(E) edge node[left]{$L(f)$} (E')
(F) edge node[right]{$L(g)$} (F')
(G) edge node[left]{$\alpha$} (G')
(E) edge node[above]{$i$} (G)
(E') edge node[below]{$i'$} (G')
(F') edge node[below]{$o'$} (G');
\end{tikzpicture}
\]
\end{itemize}
Many of the flawed applications of decorated cospans have been fixed using structured cospans
\cite[Sec.\ 6]{BC}.

We show that our new solution subsumes the old one: structured cospan double categories are always equivalent to decorated cospan double categories.  (REALLY????)

We also give sufficient conditions for a decorated cospan double category to be equivalent to a structured cospan double category. 
Suppose $\A$ has finite colimits and $F \maps (\A , +) \to (\Cat, \times)$ is a 
symmetric lax monoidal pseudofunctor.   Any such pseudofunctor gives an opfibration 
$R \maps \X \to \A$ where $\X = \int F$ is defined by the Grothendieck construction.
Let $\Rex$ be the 2-category of finitely cocomplete categories, finite-colimit-preserving
functors and natural transformations.  We show that if $F$ factors through $\mathbf{Rex}$ as
a pseudofunctor, the opfibration $R \maps \X \to \A$ is also a right adjoint.  From the accompanying left adjoint $L \maps \A \to \X$, we  construct a symmetric monoidal double category ${}_L \lCsp(\X)$ of structured cospans.  Finally, in \cref{thm:equiv} we prove that this structured cospan double category ${}_L \lCsp(\X)$ is equivalent to the decorated cospan double category $F \lCsp$.

\iffalse
To obtain a decoration on the composition of two composable decorated cospans:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,0) {$b$};
\node (C) at (2,0) {$a_2$};
\node (F) at (3,0) {$a_2$};
\node (G) at (4,0) {$b'$};
\node (H) at (5,0) {$a_3$};
\node (D) at (0.5,-0.5) {$1$};
\node (E) at (1.5,-0.5) {$F(b)$};
\node (D') at (3.5,-0.5) {$1$};
\node (E') at (4.5,-0.5) {$F(b')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(F) edge node[above]{$i'$} (G)
(H) edge node[above]{$o'$} (G)
(D) edge node [above] {$d_1$} (E)
(D') edge node [above] {$d_2$} (E');
\end{tikzpicture}
\]
we use the natural map from a coproduct to a pushout as well as the structure maps, or `laxators', that come as part of the structure of a lax monoidal functor:
\[
1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(b) \times F(b') \xrightarrow{\phi_{b,b'}} F(b+ b') \xrightarrow{F(j_{b,b'})} F(b+_{a_2} b').
\]
Using this idea, Fong constructed a symmetric monoidal category $F\textnormal{Cospan}(\A)$ which has:
\begin{enumerate}
\item{objects as those of $\A$ and}
\item{morphisms as isomorphism classes of $F$-decorated cospans, where an $F$-decorated cospan is given as above, and two $F$-decorated cospans are in the same isomorphism class if there exists an isomorphism $f \maps b \to b'$ between the apices such that the following diagrams commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,1) {$b$};
\node (B') at (1,-1) {$b'$};
\node (C) at (2,0) {$a_2$};
\node (D) at (3,0) {$1$};
\node (E) at (4,0.5) {$F(b)$};
\node (E') at (4,-0.5) {$F(b')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[below]{$i'$} (B')
(C) edge node[below]{$o'$} (B')
(B) edge node [left] {$f$} (B')
(B) edge node [right] {$\sim$} (B')
(D) edge node [above] {$d$} (E)
(D) edge node [below] {$d'$} (E')
(E) edge node [right] {$F(f)$} (E');
\end{tikzpicture}
\]
}
\end{enumerate}

As an example, let $F \maps \textsf{FinSet} \to \textsf{Set}$ be the symmetric lax monoidal functor that assigns to a finite set $b$ the (large) set of all possible graph structures on the finite set $b$, where a graph structure on $b$ is given by a diagram in $\textsf{Set}$ of the form:
\node (A) at (0,0) {$E$};
\node (B) at (1,0) {$b.$};
(A) edge[bend left] node[above]{$s$} (B)
(A) edge[bend right] node[below]{$t$} (B);
Let $b=\{ v_1,v_2 \}$ be a two element set. Then one element of the (large) set $F(b)$, which is the collection of all graph structures on the finite set $b$, is given by a single edge $e$ whose source and target are $v_1$ and $v_2$, respectively.
  [scale=.8,auto=left]
  \node [style={circle,fill=teal}] (n1) at (1,10) {$v_1$};
  \node[style={circle,fill=teal}] (n2) at (4,10)  {$v_2$};
(n1) edge node[above]{$e$} (n2);
%\node (A) at (0,0) {$v_1$};
%\node (B) at (1,0) {$v_2$};
%(A) edge node[above]{$e$} (B);
Denote this element of $F(b)$ as $d \maps 1 \to F(b)$. Let $a_1=\{ 1 \}$ and $a_2=\{2,3\}$ and define functions $i \maps a_1 \to b$ and $o \maps a_2 \to b$ by $i(1)=v_1$ and $o(2)=o(3)=v_2$. Then we have an $F$-decorated cospan: 
\node (C) at (2,0) {$a_2$};
\node (D) at (3,0) {$1$};
\node (E) at (4,0) {$F(b)$};
(D) edge node [above] {$d$} (E);
which is given by the open graph:
  [scale=.8,auto=left]
\node (a) at (-2,10) {$1$};
\node (b) at (7,10.5) {$2$};
\node (c) at (7,9.5) {$3$};
\node (i) at (-0.5,11) {$i$};
\node (o) at (5.5,11) {$o$};
  \node [style={circle,fill=teal}] (n1) at (1,10) {$v_1$};
  \node[style={circle,fill=teal}] (n2) at (4,10)  {$v_2$};
(a) edge[dashed] node[above] {$$} (n1)
(b) edge[dashed] node[below] {$$} (n2)
(c) edge[dashed] node[above] {$$} (n2)
(n1) edge node[above]{$e$} (n2);
We can compose this open graph with another whose set inputs coincide with the set of outputs of the above open graph, namely the set $a_2=\{2,3\}$. For example:
  [scale=.8,auto=left]
%\node (a) at (-2,10) {$1$};
\node (b) at (7,10.5) {$2$};
\node (c) at (7,9.5) {$3$};
%\node (i) at (-0.5,11) {$i$};
\node (o) at (8.5,11.5) {$i'$};
\node (d) at (16,10) {$4$};
\node (e) at (14.5,11.5) {$o'$};
  \node [style={circle,fill=teal}] (n1) at (10,11.5) {$v_4$};
  \node[style={circle,fill=teal}] (n2) at (10,8.5)  {$v_3$};
  \node[style={circle,fill=teal}] (n3) at (13,10)  {$v_5$};
%(a) edge[dashed] node[above] {$$} (n1)
(b) edge[dashed] node[below] {$$} (n1)
(c) edge[dashed] node[above] {$$} (n2)
(n1) edge[bend left] node[above]{$e_2$} (n3)
(n3) edge[bend left] node[below]{$e_3$} (n2)
(n2) edge[bend left] node[left]{$e_1$} (n1)
(d) edge[dashed] node[above]{$$}(n3);
This second open graph can be represented by the $F$-decorated cospan:
\node (A) at (0,0) {$a_2$};
\node (B) at (1,0) {$b'$};
\node (C) at (2,0) {$a_3$};
\node (D) at (3,0) {$1$};
\node (E) at (4,0) {$F(b')$};
(A) edge node[above]{$i'$} (B)
(C) edge node[above]{$o'$} (B)
(D) edge node [above] {$d'$} (E);
The composite of these two open graphs is then given by:
  [scale=.8,auto=left]
\node (a) at (-2,10) {$1$};
%\node (b) at (7,10.5) {$2$};
\node (c) at (10,10) {$4$};
\node (i) at (-0.5,11) {$i$};
\node (o) at (8.5,11) {$o'$};
  \node [style={circle,fill=teal}] (n1) at (1,10) {$v_1$};
  \node[style={circle,fill=teal}] (n2) at (4,10)  {$v_2$};
  \node[style={circle,fill=teal}] (n3) at (7,10)  {$v_5$};
(a) edge[dashed] node[above] {$$} (n1)
%(b) edge[dashed] node[below] {$$} (n2)
(c) edge[dashed] node[above] {$$} (n3)
(n1) edge node[above]{$e$} (n2)
(n2) edge[bend left] node[above]{$e_2$} (n3)
(n2) edge[loop below]node{$e_1$} (n2)
(n3) edge[bend left] node[below]{$e_3$} (n2);
where we identify $v_2=v_3=v_4$ in taking the pushout of the two cospans of finite sets. The composite open graph is represented by the $F$-decorated cospan:
\node (B) at (1.25,0) {$b+_{a_2}b'$};
\node (C) at (2.5,0) {$a_3$};
\node (D) at (3,0) {$1$};
\node (E) at (4,0) {$F(b+_{a_2}b')$};
(A) edge node[above]{$\psi j_b i$} (B)
(C) edge node[above]{$\psi j_{b'} o'$} (B)
(D) edge node [above] {$d''$} (E);
where $j$ is the natural map into a coproduct and $\psi$ the natural map from a coproduct into a pushout.

We can also consider the above two open graphs in parallel:
\[
\begin{tikzpicture}
  [scale=.8,auto=left]
\node (a') at (7,12.5) {$1$};
\node (b') at (16,12.5) {$2$};
\node (c') at (16,11.5) {$3$};
\node (i') at (8.5,13.5) {$i+i'$};
\node (o') at (14.5,13.5) {$o+o'$};
  \node [style={circle,fill=teal}] (n1') at (10,13) {$v_1$};
  \node[style={circle,fill=teal}] (n2') at (13,13)  {$v_2$};
\node (b) at (7,11.5) {$2$};
\node (c) at (7,10.5) {$3$};
\node (d) at (16,10.5) {$4$};
  \node [style={circle,fill=teal}] (n1) at (10,11.5) {$v_4$};
  \node[style={circle,fill=teal}] (n2) at (10,8.5)  {$v_3$};
  \node[style={circle,fill=teal}] (n3) at (13,10)  {$v_5$};
\path[->,font=\scriptsize,>=angle 90]
(a') edge[dashed] node[above] {$$} (n1')
(b') edge[dashed] node[below] {$$} (n2')
(c') edge[dashed] node[above] {$$} (n2')
(n1') edge node[above]{$e$} (n2')
(b) edge[dashed] node[below] {$$} (n1)
(c) edge[dashed] node[above] {$$} (n2)
(n1) edge[bend left] node[above]{$e_2$} (n3)
(n3) edge[bend left] node[below]{$e_3$} (n2)
(n2) edge[bend left] node[left]{$e_1$} (n1)
(d) edge[dashed] node[above]{$$}(n3);
\end{tikzpicture}
\]
which is represented by the tensor product of the above two $F$-decorated cospans:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1+a_2$};
\node (B) at (1.25,0) {$b+b'$};
\node (C) at (2.5,0) {$a_2+a_3$};
\node (D) at (3.5,0) {$1$};
\node (E) at (4.5,0) {$F(b+b')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i+i'$} (B)
(C) edge node[above]{$o+ o'$} (B)
(D) edge node [above] {$d+d'$} (E);
\end{tikzpicture}
\]

There are some subtleties to this framework; consider two decorated cospans with the same inputs and outputs.
\node (C) at (2,0) {$a_2$};
\node (F) at (3,0) {$a_1$};
\node (G) at (4,0) {$b'$};
\node (H) at (5,0) {$a_2$};
\node (D) at (0.5,-0.5) {$1$};
\node (E) at (1.5,-0.5) {$F(b)$};
\node (D') at (3.5,-0.5) {$1$};
\node (E') at (4.5,-0.5) {$F(b')$};
(F) edge node[above]{$i'$} (G)
(H) edge node[above]{$o'$} (G)
(D) edge node [above] {$d$} (E)
(D') edge node [above] {$d'$} (E');
For these two $F$-decorated cospans to be in the same isomorphism class, the following triangle is to commute:
\node (D) at (3,0) {$1$};
\node (E) at (4,0.5) {$F(b)$};
\node (E') at (4,-0.5) {$F(b')$};
(D) edge node [above] {$d$} (E)
(D) edge node [below] {$d'$} (E')
(E) edge node [right] {$F(f)$} (E');
This commutative triangle in $\Set$ in the context of the symmetric lax monoidal functor $F \maps \mathsf{FinSet} \to \Set$ says the following: given a decoration $d \in F(b)$, which is a graph structure with underlying set of vertices $b$, the function $F(f)$ pushes forward the graph structure $d$ to the graph structure $d' \in F(b')$ with underlying set of vertices $b'$, and \emph{precisely} this graph structure. The graph structure is given by set of edges of $d$. For example, if we take $b = \{v_1 ,v_2\}$ as before and let $d \in F(b)$ be given by:
  [scale=.8,auto=left]
\node (a) at (-2,10) {$1$};
\node (b) at (7,10) {$2$};
\node (i) at (-0.5,11) {$i$};
\node (o) at (5.5,11) {$o$};
  \node [style={circle,fill=teal}] (n1) at (1,10) {$v_1$};
  \node[style={circle,fill=teal}] (n2) at (4,10)  {$v_2$};
(a) edge[dashed] node[above] {$$} (n1)
(b) edge[dashed] node[below] {$$} (n2)
(n1) edge node[above]{$e$} (n2);
Let $b' = \{w_1,w_2\}$ and a define bijection $f \maps b \to b'$ by $f(v_i)=w_i$ for $i=1,2$. Then the requirement $F(f)(d)=d'$ says that $d' \in F(b')$ must be given by:
  [scale=.8,auto=left]
\node (a) at (-2,10) {$1$};
\node (b) at (7,10) {$2$};
\node (i) at (-0.5,11) {$i'$};
\node (o) at (5.5,11) {$o'$};
  \node [style={circle,fill=teal}] (n1) at (1,10) {$w_1$};
  \node[style={circle,fill=teal}] (n2) at (4,10)  {$w_2$};
(a) edge[dashed] node[above] {$$} (n1)
(b) edge[dashed] node[below] {$$} (n2)
(n1) edge node[above]{$e$} (n2);
The point to be made here is that the single edge of $d'$ must also be $e$. If we were to label it say, $e'$, there is no bijection $f \maps b \to b'$ such that the triangle on the right commutes, and hence no isomorphism between these two $F$-decorated cospans.
\begin{tikzpicture}\label{distinctisoclasses}
  [scale=.8,auto=left]
\node (D) at (9,11.5) {$1$};
\node (E) at (11,12.5) {$F(b)$};
\node (E') at (11,10.5) {$F(b')$};
\node (a) at (-2,11.5) {$1$};
\node (b) at (7,11.5) {$2$};
\node (i) at (-0.5,12.5) {$i$};
\node (o) at (5.5,12.5) {$o$};
\node (i') at (-0.5,10.5) {$i'$};
\node (o') at (5.5,10.5) {$o'$};
\node (A) at (2.5,11.5) {$\nexists F(f) \Downarrow$};
  \node [style={circle,fill=teal}] (n1) at (1,13) {$v_1$};
  \node[style={circle,fill=teal}] (n2) at (4,13)  {$v_2$};
  \node [style={circle,fill=red}] (n1') at (1,10) {$w_1$};
  \node[style={circle,fill=red}] (n2') at (4,10)  {$w_2$};
(D) edge node [above] {$d$} (E)
(D) edge node [below] {$d'$} (E')
(E) edge[dashed] node [right] {$\nexists F(f)$} (E')
(a) edge[dashed] node[above] {$$} (n1)
(b) edge[dashed] node[above] {$$} (n2)
(a) edge[dashed] node[below] {$$} (n1')
(b) edge[dashed] node[below] {$$} (n2')
(n1) edge node[above]{$e$} (n2)
(n1') edge node[above]{$e'$} (n2');
Thus these two $F$-decorated cospans constitute distinct isomorphism classes. This nuisance is amplified when viewed from a higher categorical perspective.

>>>>

An `open system' is any sort of system that can interact with the outside world.  Experience has shown that open systems are nicely modeled using cospans \cite{CourserThesis, FongThesis, PollardThesis}. A cospan in some category $\A$ is a diagram of this form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$m$};
\node (C) at (2,0) {$b$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
We call $m$ the \define{apex}, $a$ and $b$ the \define{feet}, and $i$ and $o$ the \define{legs} of the cospan.   The apex describes the system itself.  The feet describe `interfaces'  through which the system can interact with the outside world.  The legs describe how the interfaces are included in the system.   If the category $\A$ has finite colimits, we can compose cospans using pushouts: this describes the operation of attaching two open systems together in series by identifying one interface of the first with one of the second.  We can also `tensor' cospans using coproducts: this describes setting open systems side by side, in parallel.  Via these operations we obtain a symmetric monoidal double category
%%%Christina: add the notation bb{C}sp(A) since it will be central to what follows?
with cospans in $\A$ as its horizontal 1-cells \cite{Courser,Niefield}.
%%% Christina: I would be inclined to first cite Niefield and then Courser due to the chronological order.

@@

	\end{pgfonlayer}
	\begin{pgfonlayer}{edgelayer}
		\draw [style=inarrow, bend left=20, looseness=1.00] (n1) to (n2);
		\draw [style=inarrow, bend right=20, looseness=1.00] (n1) to (n3);
		\draw [style=inarrow, bend left=20, looseness=1.00] (n2) to (n4);
		\draw [style=inarrow, bend right=20, looseness=1.00] (n3) to (n4);
		\draw [style=inarrow] (n2) to (n3);
%		\draw [style=inarrow] (W) to (Water);
%		\draw [style=inarrow, bend left=40, looseness=1.00] (Water2) to (Something);
%		\draw [style=inarrow, bend right=40, looseness=1.00] (Water2) to (Something);
%		\draw [style=inarrow, bend left=40, looseness=1.00] (Something) to (A);
%		\draw [style=inarrow, bend right=40, looseness=1.00] (Something) to (B);
		\draw [style=simple] (ATL.center) to (ATR.center);
		\draw [style=simple] (ATR.center) to (ABR.center);
		\draw [style=simple] (ABR.center) to (ABL.center);
		\draw [style=simple] (ABL.center) to (ATL.center);
%		\draw [style=simple] (BTL.center) to (BTR.center);
%		\draw [style=simple] (BTR.center) to (BBR.center);
%		\draw [style=simple] (BBR.center) to (BBL.center);
%		\draw [style=simple] (BBL.center) to (BTL.center);
		\draw [style=simple] (MTL.center) to (MTR.center);
		\draw [style=simple] (MTR.center) to (MBR.center);
		\draw [style=simple] (MBR.center) to (MBL.center);
		\draw [style=simple] (MBL.center) to (MTL.center);
%		\draw [style=inputarrow] (outI) to (A);
%		\draw [style=inputarrow] (outS) to (B);
		\draw [style=inputarrow] (inI) to (n1);
		\draw [style=inputarrow] (outI') to (n4);
%		\draw [style=inputarrow] (inI') to (Water2);
%		\draw [style=inputarrow] (inS') to (Water2);
	\end{pgfonlayer}
\end{tikzpicture}
}
\]
We might hope to do this using a symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Set, \times)$ assigning to each finite set $m$ the set of all graphs with $m$ as their set of nodes. But this hope is doomed, for reasons painstakingly explained in \cite[Sec.\ 5]{BC2}. 
There is really a \emph{category} of graphs with $m$ as their set of nodes, and trying to treat it as a mere set does not work.

Here we present a solution to this problem.  Instead of basing the theory of decorated cospans on a symmetric lax monoidal functor $F \maps (\A, +) \to (\Set, \times)$, we use a symmetric lax monoidal pseudofunctor $F \maps (\A, +) \to (\Cat, \times)$.  In \cref{thm:decorated_cospans,DC}, we use this
data to construct a symmetric monoidal double category $F\lCsp$ in which:
\begin{itemize}
\item an object is an object of $\A$,
\item a vertical 1-morphism is a morphism of $\A$,
\item a horizontal 1-cell from $a$ to $b$ is a decorated cospan:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$m$};
\node (C) at (2,0) {$b,$};
\node (D) at (3,0) {$x \in F(m)$,};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
\item a 2-morphism is a \define{map of decorated cospans}: that is, a commutative
diagram
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a'$};
\node (B) at (1,0.5) {$m$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b'$};
\node (D) at (1,-0.5) {$m'$};
\node (E) at (3,0.5) {$x \in F(m)$};
\node (F) at (3,-0.5) {$x' \in F(m')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[right]{$g$} (C')
(A') edge node[above] {$i'$} (D)
(C') edge node[above] {$o'$} (D)
(B) edge node [left] {$h$} (D);
\end{tikzpicture}
\]
together with a morphism $\tau \maps F(h)(x) \to m'$ in $F(x')$.
\end{itemize}

In fact another solution to the problem is already known: the theory of structured cospans \cite{BC2,CourserThesis}.  Given a functor $L \maps \A \to \X$, a \define{structured cospan} is a cospan in $\X$ whose feet come from a pair of objects in $\A$:
\[
\begin{tikzpicture}[scale=1.2]
\node (A) at (0,0) {$L(a)$};
\node (B) at (1,1) {$x$};
\node (C) at (2,0) {$L(b).$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C)edge node[above]{$$}(B);
\end{tikzpicture}
\]
This is another way of letting the apex have more structure than the feet.   When $\A$ and $\X$ have finite colimits and $L$ preserves them, there is a symmetric monoidal double category ${}_L \lCsp(\X)$ where:
\begin{itemize}
\item an object is an object of $\A$,
\item a vertical 1-morphism is a morphism of $\A$,
\item a horizontal 1-cell from $a$ to $b$ is a diagram in $\X$ of this form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(a)$};
\node (B) at (1,0) {$x$};
\node (C) at (2,0) {$L(b)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C)edge node[above]{$o$}(B);
\end{tikzpicture}
\]
\item a 2-morphism is a commutative diagram in $\X$ of this form:
\[
\begin{tikzpicture}[scale=1.5]
\node (E) at (3,0) {$L(a)$};
\node (F) at (5,0) {$L(b)$};
\node (G) at (4,0) {$x$};
\node (E') at (3,-1) {$L(a')$};
\node (F') at (5,-1) {$L(b')$};
\node (G') at (4,-1) {$x'$};
\path[->,font=\scriptsize,>=angle 90]
(F) edge node[above]{$o$} (G)
(E) edge node[left]{$L(f)$} (E')
(F) edge node[right]{$L(g)$} (F')
(G) edge node[left]{$\alpha$} (G')
(E) edge node[above]{$i$} (G)
(E') edge node[below]{$i'$} (G')
(F') edge node[below]{$o'$} (G');
\end{tikzpicture}
\]
\end{itemize}
Many of the flawed applications of decorated cospans have been fixed using structured cospans
\cite[Sec.\ 6]{BC2}.

We show that our new solution subsumes the old one: structured cospan double categories are always equivalent to decorated cospan double categories.  (REALLY????)   %%%Christina: Not sure what this refers to. The paragraph below is more to the point. If this is supposed to provide the opposite direction, I would expect that to also hold under certain assumptions, similar to the ones below.

We also give sufficient conditions for a decorated cospan double category to be equivalent to a structured cospan double category. 
Suppose $\A$ has finite colimits and $F \maps (\A , +) \to (\Cat, \times)$ is a 
symmetric lax monoidal pseudofunctor.   Any such pseudofunctor gives an opfibration 
$U \maps \X \to \A$ where $\X = \inta F$ is defined by the Grothendieck construction.
Let $\Rex$ be the 2-category of finitely cocomplete categories, finite-colimit-preserving
functors and natural transformations.  We show that if $F$ factors through $\mathbf{Rex}$ as
a pseudofunctor, the opfibration $U \maps \X \to \A$ is also a right adjoint.  From the accompanying left adjoint $L \maps \A \to \X$, we  construct a symmetric monoidal double category ${}_L \lCsp(\X)$ of structured cospans.  Finally, in \cref{thm:equiv} we prove that this structured cospan double category ${}_L \lCsp(\X)$ is equivalent to the decorated cospan double category $F \lCsp$.
